\documentclass{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{titling}
\title{CS-102: Introduction to Computer Science}
\author{Professor: Brian Frost}
\date{Summer 2019}
\pretitle{\begin{center}\huge}
\posttitle{\end{center}}
\preauthor{\begin{center}\small}
\postauthor{\end{center}}
\predate{\begin{center}\footnotesize}
\postdate{\end{center}}
\setlength{\droptitle}{-40pt}

\begin{document}
\maketitle

\section*{Course Description}

Concepts in computer science are presented in the context of programming in C. There will also be a brief introduction to Python towards the end of the course. Students are expected to show an ability to implement the practical concepts discussed in lecture in four programming assignments. Theoretical concepts discussed in lecture will be covered on in-class quizzes each week, and a final exam will be given which covers both practical and theoretical concepts from the course.

\section*{References}

The most important reference for this course will be my website: brianlfrost.com. I will post assignments here, along with helpful documents such as practice exams. I will also upload code shown in class to a github repository at github.com/Brian-Frost-LaPlante/CS102.

There is no required text for this course. However, this text is a good C reference (albeit dense) and I will likely refer to it in class:

``The C Programming Language, $2^{\text{nd}}$ Edition" by Brian Kernighan and Dennis Ritchie

\noindent For Python, the following text is a good reference for beginners:

``Python Programming for the Absolute Beginner, $3^{\text{rd}}$ Edition" by Michael Dawson

\section*{Grading Breakdown}

\begin{itemize}

	\item \textbf{Projects (65\%)} -- Programming assignments will be assigned every week. There will be five assignments, due each Wednesday after the first week of class. This includes a final project due after the last week of class. Projects are to be sent by email to b.frost@columbia.edu. Late assignments will be penalized. Each assignment is weighted evenly.
	\item \textbf{Quizzes (20\%)} -- Short quizzes will be given every Wednesday barring the last week of class, for a total of 4 quizzes. Each quiz will last between 10 and 20 minutes, and will cover what was discussed in lecture in the past week. Each quiz is weighted evenly. You are allowed access to only your class notes during the quizzes.
	\item \textbf{Final Exam (15\%)} -- The final will be given on the last day of class (Wednesday August 7), and will last 90 minutes. It will cover material from the entire course, including both C and Python programming. A similar practice exam will be given in advance. You are allowed access to only your class notes during the final exam.

\end{itemize}

Please note that attendance is \textbf{required}, and unexcused absences will affect your grade.

\section*{Outside of Class}

I am generally responsive by email at b.frost@columbia.edu. Office hours will be held in 41 Cooper Square upon request, and open office hours will be announced during the first week of class.

\end{document}
